Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

Figure~\ref{fig:memory_hierarchy} shows the overview of one example of the hierarchy memory architecture. For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache). Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data simultaneously and improve performance. Followed by the level-1 cache, each core also has the unified, private level-2 cache for both the code and the data. The level-3 cache is the last level cache (LLC). The LLC is shared among all the cores.
The main memory is at the bottom of the memory hierarchy.
\begin{figure}[ht]
  \centering
  \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
  \caption{Computer memory hierarchy. The hierarchy is designed to minimise the access time with the relatively low cost. It is the root cause of many side-channel attacks.}\label{fig:memory_hierarchy}
\end{figure}

>>>>

Figure~\ref{fig:memory_hierarchy} shows the overview of one example of the hierarchy memory architecture. For a CPU with multiple cores, each core has two private level-1 (L1) cache: an instruction cache (iCache), and a data cache (dCache). Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data simultaneously and improve the performance. Followed by the level-1 cache, each core also has the unified, private level-2 cache for both the code and the data. The level-3 cache is the last level cache (LLC). The LLC is shared among all the cores.
The main memory is at the bottom of the memory hierarchy.
\begin{figure}[ht]
  \centering
  \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
  \caption{Computer memory hierarchy. The hierarchy is designed to minimise the access time with the relatively low cost. It is the root cause of many side-channel attacks.}\label{fig:memory_hierarchy}
\end{figure}
